Interacting with Modal Logics \\ in the Coq Proof Assistant

### 2015-01-15 Papers/InProgress/ModalLogicCoq/ModalCoq.tex
update of draft paper
Conflicts:
	Papers/InProgress/ModalLogicCoq/ModalCoq.pdf
	Papers/InProgress/ModalLogicCoq/ModalCoq.tex

The infrastructure that we have implemented for interactive and
automated reasoning in higher-order modal logics will clearly be
useful also outside philosophy; the range of potential applications is very wide.

>>>>

The infrastructure that we have implemented for interactive and
automated reasoning in higher-order modal logics will clearly be
useful also outside philosophy; the range of potential applications is
in fact very wide.
